New Evidence on the Soft Budget Constraint: Chinese Environmental Policy Effectiveness in Private versus SOEs\thanks{We would like to thank Zhao Ruili and Zhou Ling for their precious help in collecting the data from the China Environment Statistics Yearbook.}

### 2020-05-10 Paper/main.tex
Final version paper

\usepackage{amssymb,amsmath,amsfonts,eurosym,geometry,
ulem,graphicx,color,setspace,sectsty,comment,footmisc,
natbib,
pdflscape,subfigure,array,hyperref, booktabs,
threeparttable, siunitx, adjustbox,
rotating}

%https://www.stefaanlippens.net/latex-trick-customizing-captions.html
\usepackage[font=sf, labelfont={sf,bf}, margin=1cm, justification=raggedright,singlelinecheck=false]{caption}

@@

\title{New Evidence on the Chinese Environmental Policy Effectiveness in Private versus SOEs\thanks{We would like to thank the editor, anonymous reviewers for their helpful comments. We are also very greatful to Zhao Ruili and Zhou Ling for their precious help in collecting the data from the China Environment Statistics Yearbook.}}
\author{
Mathilde Maurel\thanks{CNRS, France and Centre d'Economie de la Sorbonne, Université Paris 1 Panthéon-Sorbonne, France} 
\and Thomas Pernet\thanks{Centre d'Economie de la Sorbonne, Université Paris 1 Panthéon-Sorbonne, France,
\href{mailto:t.pernetcoudrier@gmail.com}{email: t.pernetcoudrier@gmail.com} 
%email: \href{t.pernetcoudrier@gmail.com}
}
}

@@

\maketitle
\begin{abstract}
\noindent This paper analyses the efficiency of a set of environmental measures introduced by the 11th Five Years Plan (FYP) in China in 2006, using a rich and unique dataset borrowed from the Ministry of Environmental Protection (MEP) and the State Environmental Protection Agency (SEPA). The environmental regulation is rooted in two dimensions: the establishment of a list of TCZ (Two Control Zones) cities as soon as in 1998, which have the responsibility of reducing the emission of SO2, and the introduction in 2006 of an environmental target-based evaluation system, which is designed at the provincial level and enforced locally. By exploiting plausibly exogenous variation in regulatory stringency generated by the targets' system in China across provinces in 2006, we find evidence that pollution-intensive firms substantially decreased the emission of SO2, whereas SOEs (State Owned Enterprises) did not. We interpret these results as pointing to the evidence of a still ongoing SBC (Soft Budget Constraints) surrounding Chinese SOEs.

@@

The case of China offers an illustration of the dilemma many nations face between the objectives concerning development and poverty reduction on the one hand and those of fighting against pollution on the other. Environmental protection is often at odds with poverty reduction, as the steps required to reduce poverty may entail a cost in terms of pollution to build infrastructure and stimulate economies. This tradeoff holds even more in the case of China, with provinces at very different stages of economic development, as emphasized in \citet[p.196 and p.198]{Kahn2016-fi}, as follows: $``$My boss [the provincial governor] $``$$ \ldots $ $"$  knows it is hard to kill two birds [economic growth and a clean environment] with one stone in my city for now$ \ldots $ $"$, or provinces using the strategy of $``$ridding the cage of old birds (polluting firms) in favor of new ones (clean and high-skilled firms)$"$.

This metaphor evokes the two objectives which the central government is pursuing since 2000, whereas before that year, economic growth was the first and only priority for both the central and local governments. During the 2000ies, China launched a set of vigorous measures aimed at combating growth-induced pollution and environmental degradation. These reforms intended to address a growing concern of the wealthiest segments of the population, about environmental degradation, and were implemented everywhere, at different speeds. While the 10th Five Year Plan (FYP) starting in 2001 set environmental objectives at the national level, the subsequent 11th plan (2006-2010) moved the incentives for protecting the environment to the local level. It implied that for evaluating the performance of local officers, not only GDP growth rate, fiscal income, industrial value-added, exports, FDI, were considered; They were not any more binding targets with veto-power (\textit{yipiao foujue}). Environmental and energy consumption targets became veto-power targets, which every mayor had to fulfill; Otherwise, the mayor could not pass the end-year evaluation.

What external circumstances mattered for the realization of these environmental objectives? There is evidence that the cadre rotation system, that switches officials to new positions every three to four years, may be the reason why short term gains, including the extraction of rents from local dirty firms, could be prioritized over long-run ones. Studies have shown that, cities with more educated mayors reach the environmental Kuznets curve turning points at lower levels of per capita income (\cite{Zheng2014-ut}). Last but not least, holding a higher position than local officials, senior managers of state-owned firms perceived themselves as being above the local law. As a result, cities are faced with State-Owned Enterprises (SOEs) that violate environmental regulations, while at the same time gveobs that are essential to local performance.

This paper provides further evidence, by analyzing the strength of Chinese firms' policy responses to the environmental regulation introduced by the eleventh FYP. More specifically, it shows that, while private firms have been sensitive to the new environmental targets and have made significant progress towards the reduction of their emission of pollutants, SOEs have not taken similar steps. SOEs' inaction in this regard can be viewed as an outcome of the 'Soft Budget Constraint' (SBC), \cite{Kornai2003-nv}. The concept of SBC sees a straightforward application to the objective of sustainable growth: under the condition that they have rational expectations to be refinanced, as in the case of SOEs, enterprises will not be motivated to reach their objective of reducing pollution. The role of Chinese banks in rescuing SOEs and dampening the transition towards a green growth pattern has been documented in \cite{Maurel2019-ap}.

This paper revisits the issue of the SOEs' behavior and the way these firms react to environmental regulation. We start the analysis by presenting the main characteristics of the Chinese environmental policy before 2006 and up to 2010, with a special emphasis on two key components of this policy. First, the cities targeted by the central government, called 'Two Control Zone' (TCZ herefafter), 175 in number with very poor environmental performance. Second, the SO2 pollution reduction guideline provided in the eleventh FYP by the central government that aligns the motivations of the bureaucrats with the environmental policy. In sections \ref{empirical} and \ref{data}, we discuss the empirical specification and the dataset. Section \ref{analysis} summarizes the primary findings. After the policy shock, local leaders were able overall to decrease the emission of SO2, however in cities with a larger share of SOEs, this outcome did not hold.

In the subsequent section, thanks to our very rich dataset, we are able to document four different channels, beyond the SBC. Cities, where the presence of SOEs is large, do behave differently because they are predominantly non-TCZ cities. They can be cities where $``$it is hard to kill two birds [$ \ldots $ ] with one stone$"$, in other words, poorer cities. Cities with a large share of SOEs can potentially be characterized by a stronger industrial concentration and/or home firms investing less in greener projects.

First of all, TCZ cities constitute a special pool of cities that have been selected by the central government for their very poor environmental performance and are subject to a particular vigilance. We expect in these cities a stronger reaction to the environmental regulation. We also pay attention to other policies that can blur the effectiveness of the environmental regulation, noticeably Special Policies Zones (SPZ), and coastal cities. Secondly, wealthier cities are expected to comply more easily with the requirement of a lower emission of pollutants, as wealth raises the demand for cleaner growth. The estimation of Kuznets curves confirms that wealthier cities enjoy SO2 mitigation progress. Third, large firms are in the position to negotiate with local authorities, as they provide work to many employees in the region (\cite{Wang2003-ar}). This bargaining power can translate into weaker compliance with environmental regulation. Fourth, as argued in \cite{Huang1998-pi}, the lack of effective ex-post screening mechanisms in large corporations makes them tend to choose safer innovative projects. In contrast, green projects are usually risky are more likely to be undertaken by small or private firms\footnote{ SOEs are similar to large corporations because they are usually large as well.}. The innovation channel, known also as Porter's hypothesis ( \cite{Porter1995-vr}), is investigated by analyzing the impact of environmental policies on the Total Factor Productivity (TFP). We distinguish the TFP in cities with a large presence of SOEs, a large presence of big corporations, and in TCZ \textit{versus} non-TCZ cities. Finally, the paper draws the main conclusions in section \ref{conclusion}.

\section{Environmental Policy Background} \label{policy} 
\addcontentsline{toc}{section}{Environmental Policy Background}

@@

The Chinese policymakers decided to take the environmental issue seriously after the sulfur dioxide (SO2) peak hurt the country in 1995. In no less than three years, the officials in Beijing proposed and ratified a law regulating SO2 emissions. In 1998, the '\textit{Acid Rain Control Zones and Sulfur Dioxide Pollution Control Zones}' policy, abbreviated as '\textit{Two Control Zone}' (TCZ), was implemented by the central government, to control the emissions of this pollutant. While the regulation of SO2 emissions was initially designed to be implemented at the national level, the State Council subsequently chose 175 TCZ cities with very poor environmental records to engage with more effort. Three selection criteria were decided according to the environmental performance preceding the regulations. A city was placed under scrutiny if the average annual ambient SO2 concentration was higher than the national Class II standard (0.06mg/m3), if the daily average ambient SO2 concentration exceeded the national Class III standard (0.25mg/m3)\footnote{ China uses its own air quality standard, which is less stringent than the WHO's standard. China's National Environmental Monitoring Center (CNEMC) has a real-time, hourly air quality data for major cities in China. The real-time data is available at http://www.cnemc.cn/. Major air pollutants, including SO2, NO2, and PM10, are monitored. To evaluate air quality, the Chinese government applies three classes. Class 1 means the yearly SO2 level is less than 0.02 mg/m3, or a daily average of less than 0.05mg/m3. Class 2 is less restrictive. The yearly average should not exceed 0.06 and a daily average of about 0.15. Class 3 corresponds to a bad air quality. The yearly average can exceed 0.10 mg/m3, and the daily average is 0.25. By contrast, the WHO recommends a daily average of less than 0.02mg/m3. For the record, exposure to high SO2 levels dangerously affects health. According to the WHO "SO2 can affect the respiratory system and the functions of the lungs and causes irritation of the eyes. Inflammation of the respiratory tract causes coughing, mucus secretion, aggravation of asthma, and chronic bronchitis and makes people more prone to infections of the respiratory tract".}, or if the city experienced significant SO2 emissions\footnote{ A city was designated as an acid rain control zone if:(1) its average PH value of precipitation was equal or smaller than 4.5;(2) its sulfate deposition was above the critical load(3) its SO2 emissions were large }.

These 175 cities are primarily concentrated in two areas: northern China, due to the heavy reliance on coal to power the heating system, and southern China, where the urban-industrial centres emit substantial air pollution and are the source of severe acid rains. These TCZ cities cover 1.09 million square kilometres, in 27 provinces, and they account for 11.4$\%$ of the whole of China's territory.

At the national level, the objectives were the following: the emissions of SO2 were expected to decrease successively in 2000 and 2010, and a special role was devoted to TCZ cities, which were granted the responsibility of achieving the national Class II standard of 0.06mg/m3. The quota of SO2 emissions set by the central government in 2000 should not exceed 24.6 million tonnes – compared with 23.7 million tonnes in 1997 – and emissions in 2010 were expected to decrease even more than in 2000. In 2001, the policymakers strengthened the consistency of the environmental policy called the control policy in the 10th FYP (2001-2005).

TCZ cities were allowed to use four methods to achieve pollution reduction targets. They could shut down polluting plants, install new equipment, use cleaner-burning coal and implement stringent monitoring devices. All power stations with a capacity lower than 50,000 kilowatts, or collieries fueled by coal with a sulfur content of 3$\%$, had to be shut down\footnote{ 338 small power units, 784 product lines in small cement and glass plants, 404 lines in iron and steel plants, and 1422 additional pollution sources had closed and by May 2001, 4492 high-sulfur coal mines had ceased production in the TCZ area (\cite{He2002-ga})}. Furthermore, the central government had the power to cancel construction projects that did not fit the objective of lower SO2 emissions. Industrial plants were forced to meet the environmental standards by installing higher-capacity (more expensive) pollution control equipment\footnote{ The second policy is the installation of flue gas desulfurization (FGD) equipment on new and existing coal-fired power plants. At the end of 2005, FGD equipment had been installed on 46.2 GW of coal-fired electricity generation capacity—12 percent of the total, see \cite{Cao2009-sv}}. Finally, the government carefully monitored the purchase of fuel oil by firms located in TCZ cities. The transportation department was given the charge of supplying fuel oil with a sulfur concentration of less than 2$\%$ or coal with a sulfur concentration of less than 1$\%$.

Table \ref{table_1} reports the emissions of SO2 during three subsequent FYPs, from 1998 to 2010. The emissions of SO2 rose again after a short drop by -2$\%$ in 1998-2001. By the end of 2000, 102 TCZ cities reached the national Class II standard\footnote{ 84.3$\%$ of the most polluting firms achieved the national target in terms of SO2 emissions (China Environment Yearbook, 2001)}. The entry of China into the WTO in 2001 launched a process of massive industrialisation, economic growth and reduction of poverty, which was at odds with the achievement of the objective of stricter control over pollution. The consequences of the lack of coordination and the focus on economic growth from the local governments led to a historical peak of SO2 emissions in 2005, which rose by a factor of 45$\%$  over 2002-2005.

The poor results of the environmental policy were attributed to the design of the policy itself. Its main flaw was that the objectives set at the national level were not restrictive enough at the local level. As a result economic growth was strongly emphasised by the central government, which did not provide local municipalities with the incentives to enforce not only economic growth, but also control over pollution. Most of the time, those objectives turned out to be contradictory and could not be achieved contemporaneously (\cite{Barbier2019-ce,Brajer2011-wc,Grossman1995-fb,Lee2015-pw}).

\begin{table}[!htb] \centering
\caption{\\ SO2 reduction (\%) during the subsequent FYPs}
\label{table_1}
\begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
\begin{tabular}{lrrrr}
\toprule
             Cities &  1998-2001 &  2002-2005 &  2006-2010 &  Target \\
\midrule
             No TCZ &     21 &     64 &    -11 &  -6 \\
                TCZ &     -7 &     38 &    -15 & -16 \\
 $\text{No Dominated SOE}^ a$ &    -31 &     30 &    -16 & -10 \\
 $\text{Dominated SOE}^ a$ &      6 &     21 &    -17 & -12 \\
        Full Sample &     -2 &     45 &    -13 & -10 \\

\bottomrule
\end{tabular}
\end{adjustbox}
\begin{tablenotes} 
 \small 
 \item 
Sources: Author's own computation \\
The list of TCZ is provided by the State Council, 1998.
"Official Reply to the State Council Concerning Acid Rain Control Areas
and Sulfur Dioxide Pollution Control Areas".
The information about the SO2 level are collected using various editions
of the China Environment Statistics Yearbook.
We compute the reduction of SO2 emission using the same methodology
as Chen and al.(2018). \\
$a$ (No) Dominated SOEs cities refer to cities where the 
(output, capital, employment) share of SOEs is (below) above a critical threshold, for instance the 60th decile

@@

In 2006, the central government reconsidered its strategy, changing from a top-down to a bottom-up approach. Echoing the academic literature\footnote{\cite{Dewatripont1999-nq,Alesina2007-xp} are among the first to argue that the features of the mandated tasks largely drive bureaucrats' performance and efforts. The missions must be embedded in a precise interpretation scheme and be linked to performance measures. According to \cite{Alesina2008-eq}, bureaucrats choose their effort level according to two parameters: a concrete objective to reach and the weight of each task in the likelihood to move up the hierarchical leadership ladder.}, which has provided extensive research on the motivations of bureaucrats to implement a policy, the two main differences introduced in the 11th FYP (2006-2010) compared with the previous FYP (2001-2005) are the formulation of a clear pollution reduction guideline for the Chinese provinces and the introduction of an environmental target-based evaluation system for the promotion and career achievement of local officials. This target-based evaluation system aims at promoting the efforts toward the objectives considered to be priorities by the central government. It provides a tool for measuring the success of the local administration, making them accountable. The threat imposed by Beijing forces the mayors and party secretaries to adhere to the national policy. These new incentives are strongly emphasized in \cite{Kahn2015-ok}, who consider that they bear a large responsibilities in the success of the new regulation.

This new focus on environmental concerns from both the central and local governments was followed by immediate and measurable consequences: over 2006 to 2010 the average growth rate of SO2 emissions fell by -13$\%$ (full sample) as reported in table \ref{table_1}, and most TCZ cities (95$\%$ ) were able to reach the national Class II standard SO2 concentration, with no cities reporting values above the national Class III standard (\cite{Ministry_of_Environmental_Protection_of_the_Peoples_Republic_of_China2011-oi}). Local officials in TCZ cities paid more attention to the environmental prejudice of economic growth, they faced a more demanding target: -16$\%$ (TCZ cities) as compared with -6$\%$ (non-TCZ cities) and performed better with respect to the objective, achieving a SO2 reduction of -15$\%$, while non-TCZ cities reached only -11$\%$.

\section{Empirical Specification} \label{empirical}
\addcontentsline{toc}{section}{Empirical Specification}

Our identification strategy is based upon the qualitative change in the environmental strategy from a top-down to a bottom-up approach in 2006, which split the time span into two sub-periods: 2001-2005 corresponding to the 10th FYP and 2006-2010 corresponding to the 11th FYP. $target_i$ - our treatment variable - is a measure of the intensity of the policy: the reduction mandate from 2006 onwards, available at the provincial level, which therefore allows for geographical differences in treatment intensity. From the information on target available at the province level we proxy the intensity of the regulation at the city level (see below).

One concern is the influence of the most polluting industries on the probability for a given city to be provided with a more stringent reduction mandate. If such a relationship holds, it results in an endogeneity bias to be addressed: the environmental policy influences the pattern of SO2 emissions, while the share of the most polluting industries determines the other way around the level of pollution and the probability of being required to address this level of pollution in a more stringent way. We add an interaction term, which is the $target_i$ policy times the 11th FYP period times a dummy capturing the most polluting industries in China.

>>>>

%%% Guideline
% https://drive.google.com/open?id=1pPEa_nDLFMKmY97AKQXVTuxP6pbvMmdD
% Exemple: https://link.springer.com/article/10.1007/s11127-020-00799-1
% https://www.springer.com/journal/11127/submission-guidelines?IFA

\usepackage{amssymb,amsmath,amsfonts,eurosym,geometry,
ulem,graphicx,color,setspace,sectsty,comment,footmisc,
natbib,
pdflscape,subfigure,array,hyperref, booktabs,
threeparttable, siunitx, adjustbox,
rotating,
endnotes, %%% footnotes end of main text
endfloat %% table at the end https://caligari.dartmouth.edu/doc/texmf-dist/doc/latex/endfloat/endfloat.pdf
}

\DeclareDelayedFloatFlavor{sidewaystable}{table} %%% Page 8, doc sideways table with endfloat
\let\footnote=\endnote %%% Footnate end main text
%https://www.stefaanlippens.net/latex-trick-customizing-captions.html
\usepackage[font=sf, labelfont={sf,bf}, margin=1cm, justification=raggedright,singlelinecheck=false]{caption}

@@

\title{New Evidence on the Chinese Environmental Policy Effectiveness in Private versus SOEs\thanks{The authors are grateful to William F. Shughart II and two anonymous reviewers, whose comments improved the manuscript considerably. We are also very greatful to Zhao Ruili and Zhou Ling for their precious help in collecting the data from the China Environment Statistics Yearbook.}}
\author{
Mathilde Maurel\thanks{CNRS, France and Centre d'Economie de la Sorbonne, Université Paris 1 Panthéon-Sorbonne, France} 
\and Thomas Pernet\thanks{Centre d'Economie de la Sorbonne, Université Paris 1 Panthéon-Sorbonne, France,
\href{mailto:t.pernetcoudrier@gmail.com}{email: t.pernetcoudrier@gmail.com} 
%email: \href{t.pernetcoudrier@gmail.com}
}
}

@@

\maketitle
\begin{abstract}
\noindent This paper analyses the efficiency of a set of environmental measures introduced by the 11th Five Years Plan (FYP) in China in 2006, using a rich and unique dataset borrowed from the Ministry of Environmental Protection (MEP) and the State Environmental Protection Agency (SEPA). By exploiting plausibly exogenous variation in regulatory stringency generated by the targets' system in China across provinces in 2006, we find evidence that pollution-intensive firms substantially decreased the emission of SO2, whereas SOEs (State Owned Enterprises) did not. We interpret these results as pointing to the evidence of a still ongoing SBC (Soft Budget Constraints) surrounding Chinese SOEs.

@@

The case of China offers an illustration of the dilemma many nations face between the objectives concerning development and poverty reduction on the one hand and those of fighting against pollution on the other. Environmental protection is often at odds with poverty reduction, as the steps required to reduce poverty may entail a cost in terms of pollution to build infrastructure and stimulate economies. This trade-off holds even more in the case of China, with provinces at very different stages of economic development, as emphasized in \citet[p.196 and p.198]{Kahn2016-fi}, as follows: $``$My boss [the provincial governor] $``$$ \ldots $ $"$  knows it is hard to kill two birds [economic growth and a clean environment] with one stone in my city for now$ \ldots $ $"$, or provinces using the strategy of $``$ridding the cage of old birds (polluting firms) in favor of new ones (clean and high-skilled firms)$"$.

This metaphor evokes the two objectives which the central government is pursuing since 2000, obeying a model of federalism which is unique: characterized by its dualism  (\citealt{Vahabi1995-fm}), by a specific trade-off between political cost and economic benefit, and finally by the still ongoing planning of the economy and concomitant liberalization of market forces (\citealt{Berglof1998-oc, Qian1998-yf}). As a pure product of these characteristics, the 10th Five Year Plan (FYP) starting in 2001 set environmental objectives at the national level, while the subsequent 11th plan (2006-2010) moved the incentives for protecting the environment to the local level. The emphasis was switched from growth to pollution, implying that in the evaluation of the performance of local officers, GDP growth rate, fiscal income, industrial value-added, exports, foreign direct investment (FDI), were not any more binding targets with veto-power (\textit{yipiao foujue}). Conversely, environmental and energy consumption targets became veto-power targets, which every mayor had to fulfill; Otherwise, the mayor could not pass the end-year evaluation.

Has this model delivered its expected outcomes? This paper provides an answer to this question. It stresses the relative efficiency of state regulation by highlighting the strength of Chinese cities’ policy-induced responses. Moreover, it also shows that, while cities with a lower of share of SOEs have been sensitive to the new environmental targets and have made significant reductions in their emissions of pollutants, State-Owned Enterprises (SOEs) dominated cities have not taken similar steps. Their inaction in this regard can be viewed as an outcome of the 'Soft Budget Constraint' (SBC) (\citealt{Kornai2003-nv}). It is a term initially coined by Janos Kornai (\citeyear{Kornai1993-kg, Kornai1995-cu, Kornai1998-ek, Kornai2001-bw}), who referred to the phenomenon of bailing-out loss-making firms\footnote{The role of Chinese banks in rescuing SOEs and dampening the transition towards a green growth pattern has been documented in \cite{Maurel2019-ap}} that consequently undermines ex-ante incentives.

The concept of the SBC sees a straightforward application to the objective of sustainable growth: under the condition that they have rational expectations to be bailed out, as in the case of SOEs, enterprises will not be motivated to reach their objective of reducing pollution. What external circumstances, beyond the SBC, mattered for the realization of these environmental objectives? There is evidence that the cadre rotation system, that switches officials to new positions every three to four years, may be the reason why short term gains, including the extraction of rents from local dirty firms, could be prioritized over long-run ones. Studies have shown that, cities with more educated mayors reach the environmental Kuznets curve turning points at lower levels of per capita income (\citealt{Zheng2014-ut}). Last but not least, holding a higher position than local officials, senior managers of state owned firms perceived themselves as being above the local law. As a result, cities are faced with SOEs that violate environmental regulations, while at the same time generating jobs that are essential to local performance.

This paper revisits the issue of the cities' behavior and the way they react to environmental regulation. We start the analysis by presenting the main characteristics of the Chinese environmental policy before 2006 and up to 2010, with a special emphasis on two key components of this policy. First, the cities targeted by the central government, called 'Two Control Zone' (TCZ hereafter), 175 in number with very poor environmental performance. Second, the SO2 pollution reduction guideline provided in the eleventh FYP by the central government that aligns the motivations of the bureaucrats with the environmental policy. In sections \ref{empirical} and \ref{data}, we discuss the empirical specification and the data set. Section \ref{analysis} summarizes the primary findings. After the policy shock, local leaders were able overall to decrease the emission of SO2, however in cities with a larger share of SOEs, this outcome did not hold.

In the subsequent section, thanks to our very rich data set, we are able to document four different channels, beyond the SBC. SOEs dominated cities can behave differently because they are predominantly (or not) non-TCZ cities. They can be (or not) cities where $``$it is hard to kill two birds [$ \ldots $ ] with one stone$"$, in other words, poorer (or wealthier) cities. Cities with a large share of SOEs can potentially be characterized by a stronger industrial concentration and/or home firms investing less in greener projects.

First of all, TCZ cities constitute a special pool of cities that have been selected by the central government for their very poor environmental performance and are subject to a particular vigilance. We expect in these cities a stronger reaction to the environmental regulation. We also pay attention to other policies that can blur the effectiveness of the environmental regulation, noticeably Special Policies Zones (SPZ), and coastal cities. Secondly, wealthier cities are expected to comply more easily with the requirement of a lower emission of pollutants, as wealth raises the demand for cleaner growth. The estimation of Kuznets curves confirms that wealthier cities enjoy SO2 mitigation progress. Third, large firms are in the position to negotiate with local authorities, as they provide work to many employees in the region (\citealt{Wang2003-ar}). This bargaining power can translate into weaker compliance with environmental regulation. Fourth, as argued in \cite{Huang1998-pi}, the lack of effective ex-post screening mechanisms in large corporations makes them tend to choose safer innovative projects. In contrast, green projects are usually risky are more likely to be undertaken by small or private firms\footnote{ SOEs are similar to large corporations because they are usually large as well.}. The innovation channel, known also as Porter's hypothesis (\citealt{Porter1995-vr}), is investigated by analyzing the impact of environmental policies on the Total Factor Productivity (TFP). We distinguish the TFP in cities with a large presence of SOEs, a large presence of big corporations, and in TCZ \textit{versus} non-TCZ cities. Finally, the paper draws the main conclusions in section \ref{conclusion}.

\section{Environmental policy background} \label{policy} 
\addcontentsline{toc}{section}{Environmental policy background}

@@

The Chinese policymakers decided to take the environmental issue seriously after the sulfur dioxide (SO2) peak hurt the country in 1995. In no less than three years, the officials in Beijing proposed and ratified a law regulating SO2 emissions. In 1998, the '\textit{Acid Rain Control Zones and Sulfur Dioxide Pollution Control Zones}' policy, abbreviated as '\textit{Two Control Zone}' (TCZ), was implemented by the central government, to control the emissions of this pollutant. While the regulation of SO2 emissions was initially designed to be implemented at the national level, the State Council subsequently chose 175 TCZ cities with very poor environmental records to engage with more effort. Three selection criteria were decided according to the environmental performance preceding the regulations. A city was placed under scrutiny if the average annual ambient SO2 concentration was higher than the national Class two standard (0.06mg/m3), if the daily average ambient SO2 concentration exceeded the national Class three standard (0.25mg/m3)\footnote{China uses its own air quality standard, which is less stringent than the WHO's standard. China's National Environmental Monitoring Center (CNEMC) has a real-time, hourly air quality data for major cities in China. The real-time data is available at http://www.cnemc.cn/. Major air pollutants, including SO2, NO2, and PM10, are monitored. To evaluate air quality, the Chinese government applies three classes. Class one means the yearly SO2 level is less than 0.02 mg/m3, or a daily average of less than 0.05mg/m3. Class two is less restrictive. The yearly average should not exceed 0.06 and a daily average of about 0.15. Class three corresponds to a bad air quality. The yearly average can exceed 0.10 mg/m3, and the daily average is 0.25. By contrast, the WHO recommends a daily average of less than 0.02mg/m3. For the record, exposure to high SO2 levels dangerously affects health. According to the WHO "SO2 can affect the respiratory system and the functions of the lungs and causes irritation of the eyes. Inflammation of the respiratory tract causes coughing, mucus secretion, aggravation of asthma, and chronic bronchitis and makes people more prone to infections of the respiratory tract".}, or if the city experienced significant SO2 emissions\footnote{ A city was designated as an acid rain control zone if:(1) its average PH value of precipitation was equal or smaller than 4.5;(2) its sulfate deposition was above the critical load(3) its SO2 emissions were large }.

These 175 cities are primarily concentrated in two areas: northern China, due to the heavy reliance on coal to power the heating system, and southern China, where the urban-industrial centers emit substantial air pollution and are the source of severe acid rains. These TCZ cities cover 1.09 million square kilometers, in 27 provinces, and they account for 11.4$\%$ of the whole of China's territory.

At the national level, the objectives were the following: the emissions of SO2 were expected to decrease successively in 2000 and 2010, and a special role was devoted to TCZ cities, which were granted the responsibility of achieving the national Class two standard of 0.06mg/m3. The quota of SO2 emissions set by the central government in 2000 should not exceed 24.6 million tonnes – compared with 23.7 million tonnes in 1997 – and emissions in 2010 were expected to decrease even more than in 2000. In 2001, the policymakers strengthened the consistency of the environmental policy called the control policy in the 10th FYP (2001-2005).

TCZ cities were allowed to use four methods to achieve pollution reduction targets. They could shut down polluting plants, install new equipment, use cleaner-burning coal and implement stringent monitoring devices. All power stations with a capacity lower than 50,000 kilowatts, or collieries fueled by coal with a sulfur content of 3$\%$, had to be shut down\footnote{ 338 small power units, 784 product lines in small cement and glass plants, 404 lines in iron and steel plants, and 1422 additional pollution sources had closed and by May 2001, 4492 high-sulfur coal mines had ceased production in the TCZ area (\citealt{He2002-ga})}. Furthermore, the central government had the power to cancel construction projects that did not fit the objective of lower SO2 emissions. Industrial plants were forced to meet the environmental standards by installing higher-capacity (more expensive) pollution control equipment\footnote{ The second policy is the installation of flue gas desulfurization (FGD) equipment on new and existing coal-fired power plants. At the end of 2005, FGD equipment had been installed on 46.2 GW of coal-fired electricity generation capacity—12\% of the total, see \cite{Cao2009-sv}}. Finally, the government carefully monitored the purchase of fuel oil by firms located in TCZ cities. The transportation department was given the charge of supplying fuel oil with a sulfur concentration of less than 2$\%$ or coal with a sulfur concentration of less than 1$\%$.

Table \ref{table_1} reports the emissions of SO2 during three subsequent FYPs, from 1998 to 2010. The emissions of SO2 rose again after a short drop by -2$\%$ in 1998-2001. By the end of 2000, 102 TCZ cities reached the national Class two standard\footnote{ 84.3$\%$ of the most polluting firms achieved the national target in terms of SO2 emissions (China Environment Yearbook, 2001)}. The entry of China into the WTO in 2001 launched a process of massive industrialization, economic growth and reduction of poverty, which was at odds with the achievement of the objective of stricter control over pollution. The consequences of the lack of coordination and the focus on economic growth from the local governments led to a historical peak of SO2 emissions in 2005, which rose by a factor of 45$\%$ over 2002-2005.

The poor results of the environmental policy were attributed to the design of the policy itself. Its main flaw was that the objectives set at the national level were not restrictive enough at the local level. As a result economic growth was strongly emphasized by the central government, which did not provide local municipalities with the incentives to enforce not only economic growth, but also control over pollution. Most of the time, those objectives turned out to be contradictory and could not be achieved contemporaneously (\citealt{Barbier2019-ce,Brajer2011-wc,Grossman1995-fb,Lee2015-pw}).

\begin{table}[!htb] \centering
\caption{\\ SO2 reduction (\%) during the subsequent FYPs}
\label{table_1}
\begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
\begin{tabular}{lrrrr}
\toprule
             Cities &  1998-2001 &  2002-2005 &  2006-2010 &  Target \\
\midrule
             No TCZ &     21.00\% &     64.00\% &    -11.00\% &  -5.00\% \\
                TCZ &     -7.00\% &     38.00\% &    -15.00\% & -15.00\% \\
  $\text{No Dominated SOE}^ a$ &    -27.00\% &     33.00\% &    -15.00\% &  -9.00\% \\
     $\text{Dominated SOE}^ a$ &     11.00\% &     24.00\% &    -15.00\% & -12.00\% \\
        Full Sample &     -2.00\% &     45.00\% &    -13.00\% & -10.00\% \\

\bottomrule
\end{tabular}
\end{adjustbox}
\begin{tablenotes} 
 \small 
 \item 
Sources: Author's own computation \\
The list of TCZ is provided by the State Council, 1998.
"Official Reply to the State Council Concerning Acid Rain Control Areas
and Sulfur Dioxide Pollution Control Areas".
The information about the SO2 level are collected using various editions
of the China Environment Statistics Yearbook.
We compute the reduction of SO2 emission using the same methodology
as Chen and al.(2018). \\
$a$ (No) dominated SOEs cities refer to cities where the 
(output, capital, employment) share of SOEs is (below) above a critical threshold, for instance the 60th decile

@@

In 2006, the central government reconsidered its strategy, changing from a top-down to a bottom-up approach. Echoing the academic literature\footnote{\cite{Dewatripont1999-nq,Alesina2007-xp} are among the first to argue that the features of the mandated tasks largely drive bureaucrats' performance and efforts. The missions must be embedded in a precise interpretation scheme and be linked to performance measures. According to \cite{Alesina2008-eq}, bureaucrats choose their effort level according to two parameters: a concrete objective to reach and the weight of each task in the likelihood to move up the hierarchical leadership ladder.}, which has provided extensive research on the motivations of bureaucrats to implement a policy, the two main differences introduced in the 11th FYP (2006-2010) compared with the previous FYP (2001-2005) are the formulation of a clear pollution reduction guideline for the Chinese provinces and the introduction of an environmental target-based evaluation system for the promotion and career achievement of local officials. This target-based evaluation system aims at promoting the efforts toward the objectives considered to be priorities by the central government. It provides a tool for measuring the success of the local administration, making them accountable. The threat imposed by Beijing forces the mayors and party secretaries to adhere to the national policy. These new incentives are strongly emphasized in \cite{Kahn2015-ok}, who consider that they bear a large responsibility in the success of the new regulation.

This new focus on environmental concerns from both the central and local governments was followed by immediate and measurable consequences: over 2006 to 2010 the average growth rate of SO2 emissions fell by -13$\%$ (full sample) as reported in table \ref{table_1}, and most TCZ cities (95$\%$ ) were able to reach the national Class two standard SO2 concentration, with no cities reporting values above the national Class three standard (\citealt{Ministry_of_Environmental_Protection_of_the_Peoples_Republic_of_China2011-oi}). Local officials in TCZ cities paid more attention to the environmental prejudice of economic growth, they faced a more demanding target: -15$\%$ (TCZ cities) as compared with -5$\%$ (non-TCZ cities) and performed better with respect to the objective, achieving a SO2 reduction of -15$\%$, while non-TCZ cities reached only -11$\%$.

\section{Empirical specification} \label{empirical}
\addcontentsline{toc}{section}{Empirical Specification}

Our identification strategy is based upon the qualitative change in the environmental strategy from a top-down to a bottom-up approach in 2006, which split the time span into two sub-periods: 2001-2005 corresponding to the 10th FYP and 2006-2010 corresponding to the 11th FYP. $target_i$ - our treatment variable - is a measure of the intensity of the policy: the reduction mandate from 2006 onward, available at the provincial level, which therefore allows for geographical differences in treatment intensity. From the information on target available at the province level we proxy the intensity of the regulation at the city level (see below).

One concern is the influence of the most polluting industries on the probability for a given city to be provided with a more stringent reduction mandate. If such a relationship holds, it results in an endogeneity bias to be addressed: the environmental policy influences the pattern of SO2 emissions, while the share of the most polluting industries determines the other way around the level of pollution and the probability of being required to address this level of pollution in a more stringent way\footnote{Another potential bias results from the fact that City-sectors more severely affected by the regulation may exit the market. In this case, the regression will impute an decreased pollution to the regulation. city-sectors level observations in our data set allow us to probe this eventuality by investigating various samples that operated throughout the entire period (stayers) or not. Our results are robust and available upon request.}. We add an interaction term, which is the $target_i$ policy times the 11th FYP period times a dummy capturing the most polluting industries in China.
